\chapter{Introduction}

\section{Objectives and Contributions}
With the overall task being the development of an Android application to monitor skin spots, we can break this down further, grouping the three core tasks into Technical, Evaluation and Publishing.
\begin{enumerate}
    \item \textbf{Technical Tasks:}
    \begin{enumerate}
        \item The user can add and name new spots, subsequently, the user can add new images to a spot.
        \item The user is able to compare two images of a spot on the same screen.
        \item The ability to email both pictures to a doctor from within the app.
        \item Educational information screens towards skin cancer signs and usage of the app.
    \end{enumerate}
    \item \textbf{Evaluation Tasks:}
    \begin{enumerate}
        \item Performing Alpha and Beta testing phases for bug fixing and app improvements.
        \item Carry out a usability analysis with known human factor assessment methodologies.
    \end{enumerate}
    \item \textbf{Publishing Tasks:}
    \begin{enumerate}
        \item Reworking of the TrackYourSpot website to accommodate for both the iOS and Android versions of the app.
        \item Publishing a stable version of the app on the Android Play Store.
    \end{enumerate}
\end{enumerate}

\section{Definition of Terms}
Some of the language used in this report can appear confusing for people unfamiliar with the Android platform or specifically Android development. These terms are used continually throughout the report so it is recommended to pay close attention to the following definitions:
\begin{itemize}
    \item \textbf{Activity} - Interchangeable with class
    \item \textbf{Fragment} - Interchangeable with class
    \item \textbf{XML Layout} -
    \item \textbf{SDK} -
    \item \textbf{API} -
    \item \textbf{Intent} -
\end{itemize}

Throughout the report, Activities will occasionally be referred to by their implementation class name, for example \emph{CompareScreen} refers to the spot comparison screen, while \emph{SpotImageList} refers to the screen displaying all the images of a same spot.

\section{Background}

\section{Related Work}

\section{Previous Work}



\section{Report Structure}
The content of this report will be the following:
\begin{itemize}
    \item \textbf{Chapter 2 - Design: }A collection of User Interface app sketches, justification for design decisions of the main screens and specific UI features, as well as interactions and animations used within the app.
    \item \textbf{Chapter 3 - Architecture and Implementation: }This chapter will delve into the technical challenges of the task. Including choices for object architecture, alternative and/or unsuccessful approaches, flow of data and core algorithms.
    \item \textbf{Chapter 4 - Deployment: }Everything involved with publishing and branding of the app, also contains a section dedicated to the TrackYourSpot website.
    \item \textbf{Chapter 5 - User Testing and Evaluation: } Exploring the Human Factor element of the project. Analysis and results of usability testing methods and evaluation of these.
    \item \textbf{Chapter 6 - Conclusion: }Overall result of the project, limitations, lessons learnt and other thoughts.
\end{itemize}